### 2013-01-19 edupar-13/410.tex
410.tex: "invoke vanish()" -> "exit" to avoid a forward ref.

Widely regarded as the most difficult concurrency problem in the project
is that of coordinating a parent and a child task that ``simultaneously''
invoke \x{vanish()}:
when a task completes,
live children and exited zombies must be handed off
to the task's parent or to the system's \x{init} process,
at a time when the task's parent may itself be
exiting;
meanwhile, threads in tasks that receive new children
may need to be awakened from the \x{wait()} system call.
Due to design constraints imposed by other parts of the kernel specification,
solutions which are not carefully designed
are prone to data races or deadlocks.

>>>>

Widely regarded as the most difficult concurrency problem in the project
is that of coordinating a parent and a child task that ``simultaneously''
exit:
% invoke \x{vanish()}:
when a task completes,
live children and exited zombies must be handed off
to the task's parent or to the system's \x{init} process,
at a time when the task's parent may itself be
exiting;
meanwhile, threads in tasks that receive new children
may need to be awakened from the \x{wait()} system call.
Due to design constraints imposed by other parts of the kernel specification,
solutions which are not carefully designed
are prone to data races or deadlocks.
